Jilbert's Distinction Centrality

### 2025-01-26 index.qmd
make it so

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   source("distinction.R")
```

@@

   tab.cent <- function(x) { #table function
   library(kableExtra)
   t <- kbl(x, 
       digits = 2, row.names = FALSE,
       col.names = c("Node", "Distinction", "Status", "Constraint")) %>% 
      kable_styling(bootstrap_options = c("hover", "condensed", "responsive"))
   return(t)
   }

```

@@

@@

>>>>

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   source("distinction.R")
```

@@

   tab.cent <- function(x, d = 3) { #table function
   library(kableExtra)
   t <- kbl(x, 
       digits = d, row.names = FALSE,
       col.names = c("Node", "Distinction", "Status", "Constraint")) %>% 
      kable_styling(bootstrap_options = c("hover", "condensed", "responsive"))
   return(t)
   }
```

@@

```{r}
#| fig-cap: "Small World Graph."
#| fig-height: 5
#| fig-width: 5
   set.seed(1234)
   g6 <- sample_smallworld(dim = 1, 7, 2, 0.05)
   plot.graph(g6, "circle")
   ggsave(here("Plots", "sw.png"), width = 6, height = 6)
```

```{r}
#| tbl-cap: "Distinction Centrality Scores of Nodes in a Small World Graph."
   tab.cent(distinction(g6))
```

@@

```{r}
   p <- seq(0.1, 0.9, 0.01)
   r <- rep(0, length(p))
   for (i in 1:length(p)) {
      set.seed(123)
      g <- sample_smallworld(dim = 1, 15, 3, p[i]) 
      d <- distinction(g)$u
      b <- betweenness(g)
      r[i] <- cor(d, b)
      }
   dat <- data.frame(p, r)
   ggscatter(data = dat, "p", "r", add = "loess") 
```
